---
title: "Title"
subtitle: "Subtitle"
author: "Name"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
    toc_float:
      collapsed: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  cache = FALSE, cache.lazy = FALSE, autodep = TRUE, warning = FALSE, 
  message = FALSE, echo = FALSE, 
  fig.width = 8, fig.asp = 0.8, dpi = 180
  )
```

<!--#general comments===========================================================
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#
# This is [[insert description here - what it does/solve]]
#
# By: mike gaunt, michael.gaunt@wsp.com
#
# README: [[insert brief readme here]]
#-------- [[insert brief readme here]]
#
# *please use 80 character limit
# ---Tools -> Global Options -> Code -> Display -> Show Margins - > Set 80
# *please go to https://pkgs.rstudio.com/flexdashboard/articles/layouts.html
# to explore the different layouts available for the flexdashboard framework
# *please go to https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf
# to see a more complete set of RMarkdown tips and tricks
#
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

<!--#library set-up=============================================================
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#content in this section should be removed if in production - ok for dev -->
```{r}
library(tidyverse)
library(magrittr)
```

<!--#source helpers/utilities===================================================
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#content in this section should be removed if in production - ok for dev -->

```{r echo=F, eval=F}
source("./folder/example_script.r")
```

```{r echo=F, eval=TRUE}
bespoke_fnctn = function(){
  #function
}
```

<!--#define custom css or js====================================================
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#area to define custom css or js if you do not want seperate files
#--can be defined in html or markdown chunk -->

<!-- defines custom column to apply to markdown chunks-->
<style>
  .custom-column {
    flex: 1;
    text-align: left;
    padding: 10px;
  }
</style>

<style>
.my-custom-class {
  /* Your custom CSS styles here */
  background-color: #ADD8E6; /* Light blue background color */
  color: #FFFFFF; /* White text color */
  /* Add any other desired styles */
}
</style>

<!-- Defines general css -->
```{css, echo=FALSE}
pre {
  max-height: 300px;
  overflow-y: auto;
}

pre[class] {
  max-height: 300px;
  overflow-y: auto;
}
```

```{r}
plot = mtcars %>%  
  ggplot(aes(hp, disp)) + 
  geom_point()
```

<!--#source data================================================================
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#area to upload data with and to perform initial munging
#please add test data here so that others may use/unit test these scripts -->

<!--#SECTION NAME===============================================================
#use this header to make demarcations/section in code [delete this line]
#short description: e.g. show to to make in document headers -->

# Header

## Header

### Header

#### Header

### Expandable Boxes

<details>
<summary>Click to Expand</summary>

Click-to-expand boxes are a convenient way to hide content that you want to include but may not be necessary or could clutter up your Markdown document.

Example of expandable box. 

```{r}
Sys.Date()
```

</details>      

### Flex Boxes

Flexboxes enable you to arrange your text, code chunks, or outputs side-by-side, offering the flexibility to apply custom CSS styles. 

Examples include side-by-side:

+ code chunks
+ plots side by side
+ Text and plots

Example of flex displays. 

:::: {style="display: flex; justify-content: space-around; align-items: left;"}

::: {.custom-column}
Content in Column 1

```{r echo=T, eval=F}
# First code style
x <- 1:10
mean_x <- mean(x)
```

:::

::: {.custom-column}
Content in Column 2
```{r echo=T, eval=T}
# Second code style
x <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)
mean_x <- sum(x) / length(x)

print(mean_x)
```
:::

::::

### Bullet Points 

+ point 1
+ point 2
  - `point2.1`
  - point2.2
+ point 2

### Tabbed Countainers {.tabset}

Tabbed containers are great for grouping like-plots together.

The user can toggle between them and compare/contrast.

#### Tab 1

```{r}
plot
```

#### Tab 2 {.tabset}

##### Sub-Tab 2.1

```{r}
plot
```

##### Sub-Tab 2.2
```{r}
plot
```

#### {-}

### {-}

### Limit code chunk size 

Example of box explicitly limited.
```{r eval=FALSE, echo=TRUE, class.source = ".my-custom-class"}

# this is a lot of code

# this is a lot of code

# this is a lot of code

# this is a lot of code

# this is a lot of code

# this is a lot of code

# this is a lot of code

# this is a lot of code

mtcars %>%  
  ggplot(aes(hp, wt)) + 
  geom_point()


# this is a lot of code

# this is a lot of code

# this is a lot of code

# this is a lot of code

# this is a lot of code

# this is a lot of code

# this is a lot of code

# this is a lot of code

mtcars %>%  
  ggplot(aes(hp, wt)) + 
  geom_point()
```

## Plot Inputs {.tabset}

```{r}
plot
```


### fig.width = 8 {.tabset}

#### fig.asp = 0.3
```{r fig.asp = 0.3, fig.width = 8}
plot
```

#### fig.asp = 0.6
```{r fig.asp = 0.6, fig.width = 8}
plot
```

#### fig.asp = 0.8
```{r fig.asp = 0.8, fig.width = 8}
plot
```

### {-}

### fig.width = 6 {.tabset}

#### fig.asp = 0.3
```{r fig.asp = 0.3, fig.width = 6}
plot
```

#### fig.asp = 0.6
```{r fig.asp = 0.6, fig.width = 6}
plot
```

#### fig.asp = 0.8
```{r fig.asp = 0.8, fig.width = 6}
plot
```

### {-}

### fig.width = 4 {.tabset}

#### fig.asp = 0.3
```{r fig.asp = 0.3, fig.width = 4}
plot
```

#### fig.asp = 0.6
```{r fig.asp = 0.6, fig.width = 4}
plot
```

#### fig.asp = 0.8
```{r fig.asp = 0.8, fig.width = 4}
plot
```

### {-}

## {-}
<!--end-->

